Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2020-02-07 Tex/Old text/chapters/chapter02.tex
thesis update

Moreover, it is crucial to verify the compatibility between the charge controller and inverter because some models are not compatible with equipment from other manufacturers. Moreover, it is vital to select an inverter power that is lower than (or equal) the charge controller power, because the demand from the electric load causes the inverter to transfer this demand from the DC side. Then the controller can be overcharged during this operation and to burn.

>>>>

Besides that, it is crucial to verify the compatibility between the charge controller and inverter because some models are not compatible with equipment from other manufacturers. Furthermore, it is vital to select an inverter power that is lower than (or equal) the charge controller power, because the demand from the electric load causes the inverter to transfer this demand from the DC side. Then the controller can be overcharged during this operation and to burn.

### 2020-02-07 Tex/Old text/chapters/chapterverification.tex
thesis update

The first automated verification is the sizing check (line 3), if an error is found then the algorithm stops. In order to perform the sizing check, the algorithm uses Equations \eqref{eq:NTPmin}, \eqref{eq:NPSmin} and \eqref{eq:NPPmin} to verify the PV panel, Equations \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries, Equations \eqref{eq:vcvsystem}, \eqref{eq:icmin} and \eqref{eq:icicmin} to verify the charge controller; and Equations \eqref{eq:vindc}, \eqref{eq:voutac} and \eqref{eq:invcheck} to verify the inverter.

>>>>

The first automated verification is the sizing check (line 3), if an error is found then the algorithm stops. In order to perform the sizing check, the algorithm uses Equations \eqref{eq:Ecorrected}, and \eqref{eq:Pminpanel} to verify the PV panel, Equations \eqref{eq:Ebat}, \eqref{eq:DODday}, \eqref{eq:Idcbus}, \eqref{eq:Cbank}, and \eqref{eq:batcheck} to verify the batteries, Equations \eqref{eq:Icmin}, \eqref{eq:Vcmin}, \eqref{eq:vcvsystem}, \eqref{eq:icmin} and \eqref{eq:icicmin} to verify the charge controller; and Equations \eqref{eq:vindc}, \eqref{eq:voutac} and \eqref{eq:invcheck} to verify the inverter.
